\section{Glossary}
\label{sec:glossary}

\begin{description}[leftmargin=!,labelwidth=\widthof{\bfseries Data output clientxx}]
	\item[HUMS] Health and usage monitoring system(s).
	\item[The system] The HUMS we are designing and developing.
	\item[Customer] Thales.
	\item[Consumer] The recipient organisation of the system.
	\item[(End) User] An individual or organisation using the system.
	\item[HUMS instance] One installation or occurrence of the system for a specific consumer.
	\item[Client] A piece of computer hardware or software which accesses a service made available by the HUMS.
	\item[Data emitter] Anything that provides data to the HUMS through the input interface.
	\item[Data output client] Anything that receives data from the HUMS through the reporting or notification interfaces.
	\item[Analysis] The processing performed on data within the HUMS.
	\item[Event] A point of interest flagged up by an analysis system, which may result in a notification.
	\item[Notification] A message sent by the system as a result of an event being fired.
	\item[Alerting] The process of generating and delivering notifications.
	\item[Report] A message sent by the system as a result of a request from a user.
	\item[Auditing] The process of generating and returning reports.
	\item[Sensor] A single data-producing source that is monitored by the HUMS through a data emitter.
	\item[System ID] The identifier given to a group of sensors which are, for example, co-located or of the same type.
\end{description}
