\section{Customer communication}
\label{sec:communication}

Our initial communication with the Customer for this stage was in the form of a face-to-face meeting. In this meeting, we received feedback on the Initial Report. This feedback was recorded and acted upon, including extending the risk register to include more technical risks and examining the qualities of the System. Our next contact was by email, in which we sent a low fidelity prototype of the HUMS admin centre, explaining our idea of hosting a HUMS Instance as a SaaS or PaaS. The Customer said the idea was interesting and suggested some small improvements. In response to this we worked on a new iteration of the admin centre and tweaked some of the information to better explain the HUMS concept and what a SaaS solution would offer.

After each communication with the Customer, we organised group meetings within two days to discuss the feedback issued and to collaborate on any improvements to our solution we could make based upon the feedback. In our next face-to-face meeting with the Customer, we explained our architectural ideas and discussed the test application. We then went on to have a team meeting in which we planned how to monitor the test application. We then sent the Customer a series of emails detailing implementation and architectural decisions, including the qualities and views we identified and also an example of a reporting engine. The Customer replied with helpful feedback, clarifying some of the qualities and including additional qualities they felt were important to the system, along with positive feedback on the module view diagram. We incoportated this feedback and additional information into our solution and report, and improved the reporting engine to show timestamps alongside data.
