\begin{longtable}[H]{| p{0.6cm} | p{2.4cm} | p{0.5cm} | p{3cm} | p{7cm} | p{0.8cm} |}
    \hline
    \textbf{Risk ID}   & \textbf{Risk}                                             &\textbf{LS}        & \textbf{Possible Impact}                                 & \textbf{Mitigation and Contingency} & \textbf{Score} \\ \hline                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                
    \textbf{R.1}   & Short term loss of team members                  & 6       & Classification: \newline\textit{Moderate}\newline Deadline failure                                        
      &  The team can then reactively reallocate the team member's work across remaining team members. To aid with this, the team must proactively ensure that no work relating to the project is outside of team version control. Use of the scrum methodology proactively aids work reallocation, ensuring team members are aware of all assigned work. 
      & 18    \\ \hline
    \textbf{R.2}    & Long term loss of team members                   & 2 & Classification: \newline\textit{Catastrophic}\newline Deadline failure and low standard of deliverables 
    & If a team member is unavailable for an extended period, the team will react by notifying the customer and possible extending deadlines. The proactive procedures mentioned in \textbf{R.1} will also be followed to reduce the impact of this scenario.                                                                                                                                                                                                                                                                                            
    & 10    \\ \hline
    \textbf{R.3}     & Short or long term loss of resources             & 2 & Classification: \newline\textit{Catastrophic}\newline Deadline failure and loss of code base              
    & Proactive use of a source code repository, meaning code-base and history is decentralised. If the repository is lost, the data can be retrieved from the local repository copies and university backups.                                                                                                                                                                                                                                                                                                        
    & 10    \\ \hline
    \textbf{R.4}     & Team member under-performance                    & 3         & Classification: \newline\textit{Major}\newline Deadline failure and low standard  of deliverables            
    & Project plan must be feasible. The skills of the team as a whole, and individual team members must be proactively established early on and taken into account when assigning roles.                                                                                                                                                                                                                                                                                                                                                              
    & 12    \\ \hline
    \textbf{R.5}    & Misinterpretation of requirements                & 3        & Classification: \newline\textit{Major}\newline Deliverables that are not valid                                        & 
    Requirements, design and implementation strategy must be proactively verified with the customer, this process is iterative, stopping when both customer and developers are content. Any changes to those requirements must result in re-negotiated deadlines.                                                                                                                                                                                                                                                                                    
    & 12    \\ \hline
    \textbf{R.6}    & Slow response to customer queries                & 3        & Classification: \newline\textit{Major}\newline Deadline failure and  low standard of deliverables         
    & Customer has assured a two working day response where possible. Further mitigation can be achieved by proactively communicating issues well in advance of deadlines.                                                                                                                                                                                                                                                                                                                                                                            
    & 12    \\ \hline
    \textbf{R.7}     & Failure to produce required system functionality & 2 & Classification: \newline\textit{Catastrophic}\newline Wasted time and loss of marks                        
    & Customer verification of requirements can counteract this risk. System testing, to ensure all agreed upon requirements are met, will also reduce this risk.                                                                                                                                                                                                                                                                                                                                                                                      
    & 10    \\ \hline
    \textbf{R.8}     & Missing internal team deadlines                  & 5            & Classification: \newline\textit{Moderate}\newline Project falls behind due to missing dependencies                     
    & Perform critical path analysis to identify tasks which will take the longest time and which are a prerequisite to others. A greater team effort can then be assigned to these areas if it seems likely to miss a deadline or halt progress elsewhere.                                           
    & 15    \\ \hline
\end{longtable}
