\begin{longtable}[H]{ | p{3.5cm} | p{8.5cm} | p{4.5cm} |}
\hline
\cellcolor{titleColor}\textbf{Role}	       		&   \cellcolor{titleColor}\textbf{Description}                                                                   											& \cellcolor{titleColor}\textbf{Assignees}                  \\ \hline
Editors         			&   Review and format draft documentation.                                        											& JM,TD,RT                               \\ \hline
Software Architect      	&   Responsible for ensuring requirements are met, and software is consistent.         								& AJF         			 	\\ \hline
Requirements Analysis     &   Identification of customer needs and requirements.                                              								& RT,AJF,JM,TD,AIF 		\\ \hline
Developer         		&   Developing software to agreed standards.                                      		 								&  AJF,AIF,TF,TD,JM,RT,MW     \\ \hline
UX/UI Designer     		&   Accessibility, UI/UX and user stories.							                								& JM,RT,AIF           			 \\ \hline
Security     			&   Advising on relevant security standards and protocols.                                           								& TF,MW				   	 \\ \hline
Penetration Tester       	&   Test HUMS for exploits and security weaknesses.                           	                 							& AJF,TF,AIF,TD,MW              	\\ \hline
Software Tester     		&   Creating or assisting in the creation of tests.          													& AJF,AIF,TF,TD,JM,RT,MW  	 \\ \hline
Risk Manager     		&   Enhancing chance of a successful delivery.                                               									& RT.TD				   	 \\ \hline
Database Admin		&   Design of database strategies and schemas.                            		                 							& AJF,AIF,MW                           	 \\ \hline
Legal    				&   Avoiding copyright license and patent violations.          					       								& JM           				 \\ \hline
Quality Assurance             &   Ensure cohesion between system modules, analysing system performance and enforce code quality standards.  		& JM,TD				    	\\ \hline
Product Owner        		&   Representing the views of the customer.                                       										 	& RT                                        	\\ \hline
Scrum Master      		&   Ensuring Scrum process is followed by all team members, and ensuring good inter-team communication.            		& RT           				\\ \hline
\end{longtable}